
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingYeet}[7]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small #7}  \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Dynamic LaTeX command
\newcommand{\py}[1]{\textit{\%#1\%}}

\definecolor{lightGray}{gray}{0.6}
\definecolor{darkGray}{gray}{0.3}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{}{\Large Aadi Bajpai} & website: \href{https://aadibajpai.me}{aadibajpai.me}, \href{http://clashkahznlvpwfg.onion}{clashkahznlvpwfg.onion}\\
  Prospective Undergrad & email: \href{mailto:me@aadibajpai.me}{me@aadibajpai.me} \\
    \today & number: +91-93-3661-6656 \\
\end{tabular*}

\iffalse
\section{Education}%EDUCATION
  \resumeSubHeadingListStart
    \resumeSubheadingYeet
      {Delhi Public School Kalyanpur}
      {\color{lightGray}Kanpur, India}
      {All India Senior School Certificate Examination, CBSE; Percentage: 93\%}
      {\color{lightGray}May 2019}
      {All India Secondary School Examination, CBSE;  CGPA: 10/10}
      {\color{lightGray}May 2017}
      {Subjects: Physics, Chemistry \& Math with English, Computer Science \& Physical Education}
      \vspace{-3.5mm}
  \resumeSubHeadingListEnd
\fi

\section{Education}%EDUCATION
  \resumeSubHeadingListStart
    \resumeSubheading
      {Delhi Public School Kalyanpur}
      {\color{lightGray}Kanpur, India}
      {All India Senior School Certificate Examination, CBSE; Percentage: 93\%}
      {\color{lightGray}May 2019}
    \resumeSubheading
      {Delhi Public School Kalyanpur}
      {\color{lightGray}Kanpur, India}
      {All India Secondary School Examination, CBSE;  CGPA: 10/10}
      {\color{lightGray}May 2017}
      \vspace{-3.5mm}
  \resumeSubHeadingListEnd

\section{Awards \& Honours}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Grand Prize Winner, Google Code-in 2017}
      {\color{lightGray}Google}
      {\color{darkGray}\href{https://ccextractor.org}{CCExtractor Development}}
      {\color{lightGray}November 2017 - January 2018}
      \resumeItemListStart
        \item { Among fifty winners from over 3500 contestants for two months of exceptional contribution to open-source software. Won an all-expenses paid trip to Google Headquarters in California.}
        \vspace{-1mm}
        \item {Worked on a real-time Continuous Integration/Continuous Deployment platform written in Python and Flask along with Design, Research and Documentation tasks.}
     \resumeItemListEnd

     \resumeSubheading
     {Finalist, Topcoder Humblefool Charity Hackathon}
     {\color{lightGray}{Topcoder}}
     {\color{darkGray}{\'Evariste}}
     {\color{lightGray}December 2017 - February 2018}
     \resumeItemListStart
     \item \textbf{Competed among college teams} to develop an application that furthers and provides ease-of-access to programming education and resources in India.
     \vspace{-1mm}
     \item Developed \textbf{HumbleHelper} using Node.js and Material Design hosted on IBM Bluemix  which offered a bi-directional code editor and real-time teacher-student interaction and were \textbf{ranked 5th nationwide}.

     \resumeItemListEnd

     \resumeSubheading
     {Overall Winner, Comfest}
     {\color{lightGray}{Seth Anandram Jaipuria School}}
     {\color{darkGray}{Team Leader}}
     {\color{lightGray}2017, 2018}
     \resumeItemListStart
     \item Comfest is an annual, 18-year-old, techno-cultural-literary festival. It is the largest student organized school level fest in India. \textbf{The President of India} himself unveiled the Comfest brochure in 2017.
    \vspace{-1mm}
     \item Led the school team to victory for 2 consecutive years while personally having the highest overall award count. Won the events Quizart, IT Quest, Tech Talk, Crossbits and Journaltopia among others.
     \resumeItemListEnd
    \vspace{-2.5mm}
\resumeSubHeadingListEnd

\section{Computer Science Experience}%PROJECTS
  \resumeSubHeadingListStart
    \resumeSubheading
      {The SwagLyrics Project}
      {\color{lightGray}\href{https://github.com/SwagLyrics}{Open Source Organization}}
      {\color{darkGray}Founder \& Developer}
      {\color{lightGray}February 2017 - Ongoing}
      \resumeItemListStart
        \item {Researched linguistic naming conventions on Spotify and Genius to analyze patterns and bridge both the services directly without the use of an API. Authored and open-sourced a suite of Python libraries.}
    \vspace{-1mm}
        \item {SwagLyrics is 2.4x faster and more accurate than the most popular similar service\footnote{\url{https://colab.research.google.com/gist/aadibajpai/439cd358b001ae7d1ba970b68f70d92b/swaglyrics_test.ipynb}} and can fetch lyrics for a track in as less as 0.28s\footnote{\url{https://colab.research.google.com/gist/aadibajpai/06a596ad753007b0faea132e96f372e0/swaglyrics_test.ipynb}}. SwagLyrics has total \py{dlt} users growing by 1,319 per week.\footnote{Download counts: \href{https://pepy.tech/project/swaglyrics}{SwagLyrics}, \href{https://pepy.tech/project/SwSpotify}{SwSpotify}}}
    \vspace{-1.5mm}
     \resumeItemListEnd

    \resumeSubheading
      {Research Mentor, Google Summer of Code}
      {\color{lightGray}Google}
      {\color{darkGray}SwagLyrics, CCExtractor Development}
      {\color{lightGray}March 2019 - Ongoing}
      \resumeItemListStart
        \item {Mentoring Chris Wang from Columbia University in the City of New York on the SwagLyrics project \href{https://summerofcode.withgoogle.com/projects/#5694893526089728}{``Synchronizing Lyrics to Audio with Syllable Nuclei Detection"}.}
    \vspace{-1mm}
        \item {The project aims to develop a novel method of automatically synchronizing the lyrics of a song to its corresponding audio. Awarded a total grant of \$6500 by Google.}
    \vspace{-1.5mm}
     \resumeItemListEnd

    \resumeSubheading
      {Volunteer Developer \& Designer}
      {\color{lightGray}CCExtractor Development}
      {\color{darkGray}Under Carlos Fernandez Sanz, Org Admin and Founder}
      {\color{lightGray}November 2017 - Ongoing}
      \resumeItemListStart
        \item {Mentored participants as a part of Google Code-in 2018. Created various tasks and reviewed over 250 instances of tasks throughout the contest.}
    \vspace{-1mm}
        \item {\href{https://dribbble.com/shots/4422512-For-CCExtractor-Development-My-GCI-Org-3}{Designed the organization logo} and associated graphic media. Maintain the design repository along with periodic code reviews and documentation patches.}
    \vspace{1.5mm}
     \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Achievements}%SCHOLASTIC ACHIEVEMENTS
  \resumeSubHeadingListStart
    \item{Awarded \textbf{10 years' Scholar Badge} by DPS Kalyanpur for consistent \\ excellent academic performance.}
    \hfill\textit{\color{lightGray}2007 - 2018}
    \vspace{-3mm}
    \item {Qualified for the \textbf{Indian National Olympiad in Informatics 2019}.}%, 1,90,000 candidates}
    \hfill\textit{\color{lightGray}2018}
    \vspace{-3mm}
    \item {One out of the only two people in the city to successfully clear Indian \textbf{\\ Zonal Computing Olympiad 2019}.}%, 1.3 million candidates}
    \hfill\textit{\color{lightGray}2018}
    %CHECK!!
    \vspace{-3mm}
    \item {Awarded the General Proficiency Award by DPS Kalyanpur for academic excellence.}
    \hfill\textit{\color{lightGray}2015}
    \vspace{-3mm}
    \item {Won an award at \textbf{all} Model UN Conferences attended (10$+$) including the \\ Best Delegate and High Commendation award at the National Level.}
    \hfill\textit{\color{lightGray}2015 - 2018}
    \vspace{-3mm}
    \item {Won multiple National \& State Level Inter-School Quiz Competitions such as the \\ CBSE KSS Quiz and the School Quiz League (consecutively thrice).}
    \hfill\textit{\color{lightGray}2014 - 2018}
    %CHECK!!
    \vspace{-2.5mm}
\resumeSubHeadingListEnd

\section{Design Experience}%PROJECTS
  \resumeSubHeadingListStart
    \resumeSubheading
      {Automated History Archive}
      {\color{lightGray}Harvard University}
      {\color{darkGray}\href{https://scholar.harvard.edu/dell/home}{Prof. Melissa Dell, Dept. of Economics}}
      {\color{lightGray}May 2019 - Ongoing}
      \resumeItemListStart
        \item {Designing visual media to represent a high-level overview of the project and the techniques employed to generate community interest and feedback.}
    \vspace{-1.5mm}
     \resumeItemListEnd

     \resumeSubheading
      {Android App Iconography}
      {\color{lightGray}Freelance}
      {\color{darkGray}Android App Developers}
      {\color{lightGray}2017 - Ongoing}
      \resumeItemListStart
        \item {Designed the official app icons for popular Android apps on the Play Store including Hidey Hole \& Holey Light by Chainfire and KLCK by Kustom Industries that have 100,000$+$ downloads each.}
    \vspace{-1.5mm}
     \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Community Experience}%PROJECTS
  \resumeSubHeadingListStart
    \resumeSubheading
      {Member, Open Source Initiative}
      {\color{lightGray}Open Source Initiative}
      {\color{darkGray}Open Source Advocate}
      {\color{lightGray}December 2018 - Ongoing}
      \resumeItemListStart
        \item {The Open Source Initiative (OSI) is a non-profit corporation formed to educate about and advocate for the benefits of open source and to foster the open source community. OSI Affiliates include Mozilla, the Wikimedia Foundation and Linux.}
    \vspace{-1mm}
    \resumeItemListEnd
    \resumeSubheading
      {Contributor, Google$+$ Create Program}
      {\color{lightGray}Google$+$, YouTube}
      {\color{darkGray}Invited by Leanne Osborne, G$+$ Community Manager}
      {\color{lightGray}December 2016 - June 2017}
      \resumeItemListStart
        \item {Verified on YouTube and G$+$ for my ``All Things Tech" collection with more than 75,000 followers. Was put on hiatus until I become 18 due to legal policy update.}
    \vspace{-1.5mm}
     \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Programming Skills}%PROGRAMMING SKILLS
 \resumeSubHeadingListStart
    \item{\textbf{Languages}
    {: C++ {\color{lightGray}//} Python {\color{lightGray}//} HTML {\color{lightGray} // }CSS {\color{lightGray} // }Javascript {\color{lightGray} // }A Programming Language (APL)}}
        \vspace{-3mm}
    \item{\textbf{Software and Utilities}
    {: \LaTeX{} {\color{lightGray} // }Flask {\color{lightGray} // }Jinja2 {\color{lightGray} // }HAML {\color{lightGray} // }Git {\color{lightGray} // }Material Design {\color{lightGray} // }Adobe Illustrator}}
        \vspace{-1.5mm}
 \resumeSubHeadingListEnd

\section{Leadership Positions}%POSITIONS
\resumeSubHeadingListStart
      \item \textbf{Head Boy} {\color{darkGray}Student Council, DPS Kalyanpur}
      \hfill\textit{\color{lightGray}April 2018 - Present}\\

    \vspace{-1mm}

    \item \textbf{Editor-in-Chief} {\color{darkGray}Muse, DPS Kalyanpur}
        \hfill\textit{\color{lightGray}April 2018 - Present}\\

    \vspace{-1mm}

    \item \textbf{President} {\color{darkGray}Model UN Club, DPS Kalyanpur}
        \hfill\textit{\color{lightGray}April 2017 - March 2018}\\

    \vspace{-1mm}

    \item \textbf{Secretary-General }
        {\color{darkGray}Delhi Public School Kalyanpur Model UN}
        \hfill\textit{\color{lightGray}August 2017 - September 2017}\\

    \vspace{-1mm}

    \item \textbf{President} {\color{darkGray}UN Security Council, Delhi Public School Kalyanpur Model UN}
        \hfill\textit{\color{lightGray}October 2018}\\

    \vspace{-1mm}

    \item \textbf{Core Team Member} {\color{darkGray}Panorama, DPS Kalyanpur}
        \hfill\textit{\color{lightGray}August 2017 - October 2018}\\

    \vspace{-1mm}

    \item \textbf{Head of Design} {\color{darkGray}Delhi Public School Kalyanpur Model UN}
        \hfill\textit{\color{lightGray}September 2016}\\

    \vspace{-1mm}

    \item \textbf{House Prefect} {\color{darkGray}Shamrock House, DPS Kalyanpur}
        \hfill\textit{\color{lightGray}April 2016 - March 2017}\\

    \vspace{-1mm}
\resumeSubHeadingListEnd

\section{Relevant Links}
    \vspace{1mm}
    \resumeSubHeadingListStart
        \item \href{https://dribbble.com/aadibajpai}{\textbf{\underline{I Design.}}}\\
        \vspace{1mm}
        \item \href{https://github.com/aadibajpai}{\textbf {\underline{I Code. }}}\\
        \vspace{1mm}
        \item \href{https://medium.com/@aadibajpai}{\textbf {\underline{I Write.}}}\\
        \vspace{1mm}
    \resumeSubHeadingListEnd

\end{document}
